Bayesian Data Analysis, Rough Draft

### 2023-12-08 Lahman Analysis/Formal Analysis/Draft1.qmd
Added ideas to results section
Added code to allow for document render on my mac

```{r}
#Lets me load in the model that I made. Will only work on my desktop.
fit.poly <- readRDS("C:/Users/Sam/Desktop/RDS/PolyFit.rds", )
```

@@

>>>>

```{r}
#Lets me load in the model that I made. Will only work on my desktop.
#fit.poly <- readRDS("C:/Users/Sam/Desktop/RDS/PolyFit.rds", )

#Lets me load in the model for my Mac
fit.poly <- readRDS("~/Desktop/RDS/PolyFit.rds")
```

@@

## General

This section should be dedicated to talking about general fit of the model. Explore using the normals plots that we've been using with the confidence intervals to see if the parameters are near their priors. And, also explore using the trace-plots. The linegraphs that go all over the place.
